---
title: "BDA Help"
author: "awaisakram"
date: "5/12/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

This is R markdown. First of all download and install few things like [R for Windows](https://cran.r-project.org/bin/windows/base/old/3.4.3/ "R Homepage") and [R Studio](https://www.rstudio.com/products/rstudio/download/#download). First install R and then R Studio. After Installation open R studio and Create New Project and in this new project Create new file and name it as <filename>.R and save this file in working directory.
Download any dataset and from [Kaggle](https://kaggle.com) and paste it in worikng directory/Project main folder.

Now open your file with name <filename>.R and start writing code.


```{r}
# install libraries

# install.packages('caret') 
#install.packages('e1071')
#install.packages('AUC')

# and import libraries using

library(caret)
library(e1071)
library(AUC)
```

## Read Dataset

now read dataset in R that you download from kaggle, for example:

There are two csv files in working dir 
1) Credit_test.csv  
2) Credit_train.csv
```{r}
dir('./')
```

read Train and test data
```{r}
train <- read.csv("Credit_train.csv")
test <- read.csv("Credit_test.csv")
```



Columns name 
target variable is "~DEFAULT"
```{r}
colnames(train)
colnames(test)
```

Show  head of datasets
```{r}
head(train)
head(test)
```
# Algorithms on Dataset 
## Naive Bayesian

"model.Bayes" is training model that train on training dataset 
```{r}
model.Bayes <- naiveBayes(DEFAULT~., data = train)
model.Bayes
```

now find out the prediction of test data using training model "model.Bayes"
```{r}
pc <- predict(model.Bayes, test, type = "class")
# Summary of prediction 
summary(pc)


```

finding accuracy of model using confusion Matrix
```{r}
xtab <- table(pc, test$DEFAULT)
caret::confusionMatrix(xtab, positive = "Y")
```

## K Nearest Neighbors
on same dataset

```{r}
# import libraries

library(caret)
library(kknn)
library(AUC)


#remove all records with missing values
train <- na.omit(train)
test <- na.omit(test)


#train model
model.KNN <- kknn(DEFAULT~., train, test, k=5, distance = 2, scale=FALSE)


# Prediction using train model on test dataset
pc <- predict(model.KNN, test, type="raw")
# Summary of prediction
summary(pc)

# confusion matrix for accuracy
xtab <- table(pc, test$DEFAULT)
caret::confusionMatrix(xtab, positive="Y")
```